\newrefsection
\chapter{B2.a State-of-the-art and objectives}

\eu{(B2.a, B2.b: max 14 pages}
\eu{

Section a: State-of-the-art and objectives. Specify the proposal objectives in
the context of the state of the art in the research field. It should be clear
how and why the proposed work is important for the field, and what impact it
will have if successful, such as how it may open up new horizons or
opportunities for science, technology or scholarship. Specify any particularly
challenging or unconventional aspects of the proposal, including multi- or
inter-disciplinary aspects.


Section B: Methodology. Describe the proposed methodology in detail including
any key intermediate goals. Explain and justify the methodology in relation to
the state of the art. Highlight any intermediate stages where results may
require adjustments to the project planning. In case you ask that team members
are engaged by another host institution, their participation has to be fully
justified by the scientific added value they bring to the project.  }

\TODO{TARGET PAGE COUNT: 4 pages: state of art + vision; 2 pages: methodology overview; 5 pages:
WPs; 3 pages: ethics + risks}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A. State-of-art and objectives}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{State-of-art: social representations for intelligent robots}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Objectives of \project}

\subsection{Basic research objectives}

\subsection{Empirical research objectives}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interdiscplinary nature of the project}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{B. Methodology}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Overview of \project methodology}

\subsubsection{Gantt chart}

\subsubsection{Project's milestones}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Expertise of the research team}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Workpackages}

\subsubsection{WP1: \textbf{\wpOne}}

\subsubsection{WP2: \textbf{\wpTwo}}

\subsubsection{WP3: \textbf{\wpThree}}

\subsubsection{WP4: \textbf{\wpFour}}

\subsubsection{WP5: \textbf{\wpFive}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental methodology}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Risk/gain analysis}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\printbibliography

